Overlapping Batches for the Assessment of Solution Quality in Stochastic Programs

### 2014-06-16 omrp_lb_rev.tex
Remarks on comparing computational work of OMRP to MRP with bigger k
Also cleaned up the plot a little bit

	modified:   images/work_comparison.fig
	modified:   images/work_comparison.pdf
	modified:   omrp_lb_rev.tex

>>>>

\begin{figure}[htb!]
	\centering
	\includegraphics[width=.5\textwidth]{images/work_comparison}
	\caption{
		A theoretical comparison of the computational work required to get equivalent variance reduction between OMRP and MRP when the number of batches are increased.
		}
\label{fig:comp_work_comparison}
\end{figure}

A final question on computational efficiency would be whether OMRP is more efficient than nonoverlapping MRP with a larger number of batches.
In the nonoverlapping case, $\var{VG} \propto \frac{1}{k}$, so decreasing $\var{VG}$ to the level of maximally overlapping batches requires a $50\%$ increase in the number of batches, and thus a $50\%$ increase in computation time.
Again assuming average time per batch can be represented as $T(\gammab) = \gammab^p$, Figure \ref{fig:comp_work_comparison} compares the increase in computational work for OMRP for several values of $p$ with the work increase for MRP to get an equivalent decrease in variance.
We again see that OMRP is advantageous for larger values of $p$.
